\plaintitle

### 2018-04-03 paper/paper.tex
...

Online help systems are usually hard to use because of the
vocabulary problem \cite{Furnas:1987:VPH:32206.32212}.

People don't use online help
\cite{Novick:2006:WDP:1166324.1166329}.
Twitterでのアンケート: 80\% が全然使わない

When we use modern artifacts,
we shoule translate our intentions into actions required for the artifacts.
When we want to watch a movie, we may pick up a DVD disk, put it into a
DVD player, push the play button, and set up the audio and the monitor.
When we feel thirsty, we may go to the kitchen, pick up a glass, and
turn the faucet on to fill the glass with water.
All the living creatures seem to be performing such translations
between intentions and actions without difficulty, but
in the modern world, people are suffering from
serious gaps between what they want to do and what they have to do.

>>>>

When people want to perform a task using modern artifacts,
people frequently find difficulty handling them properly.
%
Manuals and help systems are usually provided, but they are 
usually hard to use because of the
vocabulary problem \cite{Furnas:1987:VPH:32206.32212}.
%
People don't use online help systems\cite{Novick:2006:WDP:1166324.1166329}.
Twitterでのアンケート: 80\% が全然使わない
% https://gyazo.com/2dd525388cce34c916638f51bad386c7

やりたいと思ったことがすぐできればどれほど嬉しいことか
そもそも検索や翻訳が必要なものであるならそれを楽にすればよい

When we use artifacts,
we shoule translate our intentions into actions required for the artifacts.
When we want to watch a movie, we may pick up a DVD disk, put it into a
DVD player, push the play button, and set up the audio and the monitor.
When we feel thirsty, we may go to the kitchen, pick up a glass, and
turn the faucet on to fill the glass with water.
All the living creatures seem to be performing such translations
between intentions and actions without difficulty, but
in the modern world, people are suffering from
serious gaps between what they want to do and what they have to do.
